\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-08-24 notes/2loopNLSM.tex
More tikz stuff.  Progress on YM writeup.

\subsection{Pions -- James}

@@

we proceed with the relaxed version of the method of
maximal cuts used above in the pion construction [\ace{is James going
  to talk about something along this line in the pions section?}].  We
find that even with the completely generic ansatz, the representation
fails to satisfy the next-to-next-to-maximal cut shown in [].
Notably, imposing the BDN power-counting constraints additionally
causes a discrepancy with the N$^2$-max cuts show in [].

\KissingTriangles

>>>>

\subsection{Pions -- James}
\label{sec:pions}

@@

Similar to the pion construction in \cref{sec:pions}, we use the
kinematic Jacobi relations to define the numerators for all cubic
graphs in terms of the two basis graphs, including allowing nontrivial
numerators on BEL diagrams.  We will simply avoid imposing
constraints that directly involve such pathological diagrams.  That
leaves us with 14 non-pathological cubic diagrams on which to impose
maximal cuts and symmetries. \ace{Do we want the graphs for these?
  Doable in tikz, but would take some time, or I can dump nice-ish
  versions from mathematica}.  Doing so, we are left with AA total
parameters in the unrestricted ansatz and BB total in the
BDN-restricted ansatz.

Proceeding to the next-to-maximal cuts, we continue to avoid BEL
diagrams.  Additionally, now that we have higher-point vertices, we
avoid diagrams in which the higher-point vertex could contain an
off-shell propagator that carries the same momenta as one of the cut
propagators, \eg \ace{Any feedback on how this looks, especially with
  the dashed lines?}
\begin{equation*}
  \begin{tikzpicture}
    \pgfmathsetmacro{\ri}{1};
    \pgfmathsetmacro{\re}{0.6};
    \pgfmathsetmacro{\ang}{35};
    \begin{feynman}
      \blob{i1}{\ang:\ri};
      \blob{i2}{180-\ang:\ri};
      \blob{i3}{180+\ang:\ri};
      \blob{i4}{-\ang:\ri};
      \blob{i5}{ $(i1)!0.5!(i2)$ };
      \ver{e1}{45:\ri+\re};
      \ver{e2}{135:\ri+\re};
      \ver{e3}{225:\ri+\re};
      \ver{e4}{-45:\ri+\re};

      \diagram{
        {[edges={ultra thick}] (e1)--(i1),
          (e2)--(i2),
          (e3)--(i3),
          (e4)--(i4),
          (i5)--(i1)--(i4)--(i3)--(i2),
          (i2) --[out=60,in=180-60] (i5),
          (i2) --[out=-60,in=180+60] (i5)
        };
      };
    \end{feynman}
  \end{tikzpicture}
  \text{ contains a contribution from }
  \begin{tikzpicture}
    \pgfmathsetmacro{\ri}{1};
    \pgfmathsetmacro{\re}{0.6};
    \pgfmathsetmacro{\ang}{35};
    \pgfmathsetmacro{\cang}{90};
    \pgfmathsetmacro{\cl}{1.1};
      \ver{i1}{\ang:\ri};
      \ver{i2}{180-\ang:\ri};
      \ver{i3}{180+\ang:\ri};
      \ver{i4}{-\ang:\ri};
      \ver{i5}{ $(i1)!0.25!(i2)$ };
      \ver{i6}{ $(i1)!0.75!(i2)$ };

      \ver{e1}{45:\ri+\re};
      \ver{e2}{135:\ri+\re};
      \ver{e3}{225:\ri+\re};
      \ver{e4}{-45:\ri+\re};

      \ver{c1}{0:\cl};
      \ver{c2}{\cang:\cl};
      \ver{c3}{2*\cang:\cl};
      \ver{c4}{3*\cang:\cl};
      \ver{ci}{$(i5)!0.5!(i1)$};
      \path let \p1 =(ci) in coordinate (c5) at (\x1,0.2){};
      \draw[ultra thick] (e1)--(i1);
      \draw[ultra thick] (e2)--(i2);
      \draw[ultra thick] (e3)--(i3);
      \draw[ultra thick] (e4)--(i4);
      \draw[ultra thick] (i5)--(i1)--(i4)--(i3)--(i2)--(i6);
      \draw[ultra thick] (i6) to[out=60,in=180-60] (i5);
      \draw[ultra thick] (i6) to[out=-60,in=180+60] (i5);
      \draw[dashed,ultra thick,blue] (0,0) -- (c1);
      \draw[dashed,ultra thick,blue] (0,0) -- (c2);
      \draw[dashed,ultra thick,blue] (0,0) -- (c3);
      \draw[dashed,ultra thick,blue] (0,0) -- (c4);
      \draw[dashed,ultra thick,blue] (c5) -- ++(90:0.7*\cl);

  \end{tikzpicture},
\end{equation*}
as it is non-trivial and beyond the scope of this paper to define
exactly what such a cut and cut contribution means.  After discarding
these types of cuts, we are left with 8 unique cut topologies to
check.  Seven of these next-to-maximal cuts are consistent with the
kinematic Jacobi relations and symmetries.  Interestingly, the
``kissing triangles'' cut,
\begin{equation*}
  \KissingTriangles \,,
\end{equation*}
cannot be satisfied by either the unrestricted or the BDN-restricted
ansatz with Jacobi relations and symmetries applied.
